### 2023-04-14 inst/reproduce_results/results.Rmd
Minor bugfixes and features

```{r adolphi, eval=TRUE}
library(ggplot2)
x.ref=c(11050,12050,13050,22050,42050)
adolphipdfs = adolphiloader(tieshifts=c(11050,12050,13050,22050,42050),plotdens = FALSE,
                            x.ref=x.ref)
lower = c(-77.53, -30.92, -12.37, 336.19, 101.51)+x.ref
upper = c(-41.09, 11.94, 21.99, 714.03, 509.08)+x.ref
means = c(-59.95, -7.04, 3.34, 521.44, 275.24)+x.ref
medians = c(-60.10, -6.42, 2.64, 532.36, 243.57)+x.ref
gg1 = ggplot(data=adolphipdfs$tie1,aes(x=x,y=y))+geom_line()+theme_bw()+xlab("GICC05 age (yb2k)")+
  ggtitle("Tie-point 1") + ylab("Density") + 
  geom_vline(aes(xintercept=x.ref[1]),color="black")+
  geom_vline(aes(xintercept=means[1]),color="blue")+
  geom_vline(aes(xintercept=lower[1]),color="red")+
  geom_vline(aes(xintercept=upper[1]),color="red")
gg2 = ggplot(data=adolphipdfs$tie2,aes(x=x,y=y))+geom_line()+theme_bw()+xlab("GICC05 age (yb2k)")+
  ggtitle("Tie-point 2") + ylab("Density") + 
  geom_vline(aes(xintercept=x.ref[2]),color="black")+
  geom_vline(aes(xintercept=means[2]),color="blue")+
  geom_vline(aes(xintercept=lower[2]),color="red")+
  geom_vline(aes(xintercept=upper[2]),color="red")
gg3 = ggplot(data=adolphipdfs$tie3,aes(x=x,y=y))+geom_line()+theme_bw()+xlab("GICC05 age (yb2k)")+
  ggtitle("Tie-point 3") + ylab("Density") + 
  geom_vline(aes(xintercept=x.ref[3]),color="black")+
  geom_vline(aes(xintercept=means[3]),color="blue")+
  geom_vline(aes(xintercept=lower[3]),color="red")+
  geom_vline(aes(xintercept=upper[3]),color="red")
gg4 = ggplot(data=adolphipdfs$tie4,aes(x=x,y=y))+geom_line()+theme_bw()+xlab("GICC05 age (yb2k)")+
  ggtitle("Tie-point 4") + ylab("Density") + 
  geom_vline(aes(xintercept=x.ref[4]),color="black")+
  geom_vline(aes(xintercept=means[4]),color="blue")+
  geom_vline(aes(xintercept=lower[4]),color="red")+
  geom_vline(aes(xintercept=upper[4]),color="red")
gg5 = ggplot(data=adolphipdfs$tie5,aes(x=x,y=y))+geom_line()+theme_bw()+xlab("GICC05 age (yb2k)")+
  ggtitle("Tie-point 5") + ylab("Density") + 
  geom_vline(aes(xintercept=x.ref[5]),color="black")+
  geom_vline(aes(xintercept=means[5]),color="blue")+
  geom_vline(aes(xintercept=lower[5]),color="red")+
  geom_vline(aes(xintercept=upper[5]),color="red")

library(ggpubr)
ggarrange(ggarrange(gg1,gg2,gg3,nrow=1),
          ggarrange(gg4,gg5,nrow=1),
          nrow=2)
# ggsave("adolphipdfs-4800x2000.eps", device=cairo_ps,width=4800,height=2400,units="px",dpi=500,limitsize=FALSE)

@@

ggp = ggplot() + theme_bw() + xlim(rev(range(results$data$age)))+
  xlab("GICC05 (yb2k)")+ylab(expression(paste(delta^18,"O (permil)")))
nevents=results$.args$events$nevents
agestarts = numeric(nevents)
for(i in 1:nevents){
  indexes = which(results$data[[paste0("psi0_",i)]]>0)
  age_i = results$data$age[indexes]
  agestarts[i]=age_i[1]
  proxy_i = results$data$proxy[indexes]
  if(i %% 2 ==0 ){
    color="red"
  }else{
    color="blue"
  }
  ggp = ggp + geom_line(data=data.frame(age_i=age_i,proxy_i=proxy_i),
                        mapping=aes(x=age_i,y=proxy_i),col=color)
}
agestarts[nevents]=last(results$data$age)
ggp = ggp + geom_vline(xintercept = agestarts,col="black",size=0.15)
print(ggp)
# ggsave("proxyplot-4800x2000.eps", device=cairo_ps,width=4800,height=2000,units="px",dpi=500,limitsize=FALSE)

@@

```{r unconstrained}
{
  library(ggplot2)

@@

```{r fixed, eval=TRUE}
fixedsims = cbind(#rep(inla.mmarginal(adolphipdfs$tie1),nsims),
                  rep(inla.mmarginal(adolphipdfs$tie2),nsims),
                  rep(inla.mmarginal(adolphipdfs$tie3),nsims),
                  rep(inla.mmarginal(adolphipdfs$tie4),nsims),
                  rep(inla.mmarginal(adolphipdfs$tie5),nsims)
                  )
synchronization = list(samples = fixedsims,nsims=nsims,
                       locations=c(#1492.50,
                                   1502.80,1532.70,1767.25,2132.40),
                       locations_unit="depth")
results_fixed = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                synchronization=synchronization,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=TRUE) ,
                print.progress=TRUE
                )
{
  gicc05=results_fixed$original.chron$age[1+1:n]
  ggd = data.frame(depth=results_fixed$data$depth,
                   mean=results_fixed$simulation$summary_sync$mean-gicc05,
                   lower=results_fixed$simulation$summary_sync$lower-gicc05,
                   upper=results_fixed$simulation$summary_sync$upper-gicc05,
                   zeros = numeric(n))
  ggp = ggplot(data=ggd,aes(x=depth)) + theme_bw()+
    #geom_line(aes(y=zeros),color="gray",linetype="dashed")+
    geom_line(aes(y=mean),col="blue")+
    geom_ribbon(aes(ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    xlab("Depth (m)") + ylab("Simulated time scale - GICC05 (years)")
  print(ggp)

@@

Synchronizing our chronologies with the Adolphi tie-points where the uncertainties is incorporated cam be done using Monte Carlo simulations. All of this can be done using the bremla function.

@@

@@

```{r events_individual, eval=FALSE}
eventnumber=13 #number between 1 and 29. specifies which transition to consider
#load data window and specifics to transition
lowerints = which.index(event_intervals$depth_int_lower.m, depth[2:length(depth)])
upperints = which.index(event_intervals$depth_int_upper.m, depth[2:length(depth)])
depth.reference = event_intervals$NGRIP_depth_m[eventnumber]
age.reference = event_intervals$GICC_age.yb2k[eventnumber]
interval = lowerints[eventnumber]:upperints[eventnumber]
transitionlabel = str_sub(event_intervals$onsetlabel[eventnumber],
                      str_locate(event_intervals$onsetlabel[eventnumber],"GI")[1])
control.linramp=list(proxy=proxy,
                     interval=interval,
                     interval.unit="index",
                     depth.reference=event_intervals$NGRIP_depth_m[eventnumber]
                     )
results_event = linrampfitter(results_sync,control.linramp)
control.transition_dating = list(label="Simulated transition")
results_event = events_depth_to_age(results_event,
                                    control.transition_dating=control.transition_dating)
{
  ggd1 = data.frame(depth=depth[interval],proxy=proxy[interval],
                    x=results_event$linramp$data$x,
                    mean=results_event$linramp$linrampfit$mean,
                    lower=results_event$linramp$linrampfit$q0.025,
                    upper=results_event$linramp$linrampfit$q0.975
                    )
  gg1 = ggplot(data=ggd1,aes(x=depth))+geom_line(aes(y=proxy),col="gray")+
    theme_bw()+ xlim(rev(range(depth[interval])))+xlab("Depth (m)")+
    ylab(expression(paste(delta^18,"O (permil)")))+ggtitle("(a) GI-11 Linear ramp fit")+
    geom_ribbon(aes(x=x,ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    geom_line(aes(x=x,y=mean),col="blue",size=0.7)

@@

>>>>

```{r adolphi, eval=TRUE}
library(ggplot2)
x.ref=c(11050,12050,13050,22050,42050)
adolphipdfs = adolphiloader(tieshifts=c(11050,12050,13050,22050,42050),
                            plotdens = FALSE,
                            x.ref=x.ref)
lower = c(-77.53, -30.92, -12.37, 336.19, 101.51)#+x.ref
upper = c(-41.09, 11.94, 21.99, 714.03, 509.08)#+x.ref
means = c(-59.95, -7.04, 3.34, 521.44, 275.24)#+x.ref
medians = c(-60.10, -6.42, 2.64, 532.36, 243.57)#+x.ref
adolphipdfs_offsets = c()
for(i in 1:5){
  adolphipdfs_offsets[[i]] = cbind(as.numeric(adolphipdfs[[i]]$x)-x.ref[i],
                                   as.numeric(adolphipdfs[[i]]$y))
  colnames(adolphipdfs_offsets[[i]]) = c("x","y")
  #adolphipdfs_offsets[[i]]$x = adolphipdfs[[i]]$x-x.ref
}

gg1 = ggplot(data=as.data.frame(adolphipdfs_offsets[[1]]),aes(x=x,y=y))+geom_line()+theme_bw()+xlab("Age offset (years)")+
  ggtitle("Tie-point 1") + ylab("Density") + 
  xlim(c(-100,100))+
  #geom_vline(aes(xintercept=x.ref[1]),color="black")+
  geom_vline(aes(xintercept=means[1]),color="blue")+
  geom_vline(aes(xintercept=lower[1]),color="red")+
  geom_vline(aes(xintercept=upper[1]),color="red")
gg2 = ggplot(data=as.data.frame(adolphipdfs_offsets[[2]]),aes(x=x,y=y))+geom_line()+theme_bw()+xlab("Age offset (years)")+
  ggtitle("Tie-point 2") + ylab("Density") + 
    xlim(c(-60,60))+
  #geom_vline(aes(xintercept=x.ref[2]),color="black")+
  geom_vline(aes(xintercept=means[2]),color="blue")+
  geom_vline(aes(xintercept=lower[2]),color="red")+
  geom_vline(aes(xintercept=upper[2]),color="red")
gg3 = ggplot(data=as.data.frame(adolphipdfs_offsets[[3]]),aes(x=x,y=y))+geom_line()+theme_bw()+xlab("Age offset (years)")+
  ggtitle("Tie-point 3") + ylab("Density") + 
    xlim(c(-60,60))+
  #geom_vline(aes(xintercept=x.ref[3]),color="black")+
  geom_vline(aes(xintercept=means[3]),color="blue")+
  geom_vline(aes(xintercept=lower[3]),color="red")+
  geom_vline(aes(xintercept=upper[3]),color="red")
gg4 = ggplot(data=as.data.frame(adolphipdfs_offsets[[4]]),aes(x=x,y=y))+geom_line()+theme_bw()+xlab("Age offset (years)")+
  ggtitle("Tie-point 4") + ylab("Density") + 
    xlim(c(-0,1000))+
  #geom_vline(aes(xintercept=x.ref[4]),color="black")+
  geom_vline(aes(xintercept=means[4]),color="blue")+
  geom_vline(aes(xintercept=lower[4]),color="red")+
  geom_vline(aes(xintercept=upper[4]),color="red")
gg5 = ggplot(data=as.data.frame(adolphipdfs_offsets[[5]]),aes(x=x,y=y))+geom_line()+theme_bw()+xlab("Age offset (years)")+
  ggtitle("Tie-point 5") + ylab("Density") + 
    xlim(c(-250,750))+
  #geom_vline(aes(xintercept=x.ref[5]),color="black")+
  geom_vline(aes(xintercept=means[5]),color="blue")+
  geom_vline(aes(xintercept=lower[5]),color="red")+
  geom_vline(aes(xintercept=upper[5]),color="red")

library(ggpubr)
ggarrange(ggarrange(gg2,gg3,nrow=1),
          ggarrange(gg4,gg5,nrow=1),
          nrow=2)
 # ggsave("adolphipdfs-no1-4800x2000.eps", device=cairo_ps,width=4800,height=2400,units="px",dpi=500,limitsize=FALSE)

@@

ggp = ggplot() + theme_bw() + xlim(rev(range(results$data$age)))+
  xlab("GICC05 (yb2k)")+ylab(expression(paste(delta^18,"O (permil)")))
nevents=results$.args$events$nevents
agestarts = numeric(nevents)
for(i in 1:nevents){
  indexes = which(results$data[[paste0("psi0_",i)]]>0)
  age_i = results$data$age[indexes]
  agestarts[i]=age_i[1]
  proxy_i = results$data$proxy[indexes]
  if(i %% 2 ==0 ){
    color="red"
  }else{
    color="blue"
  }
  ggp = ggp + geom_line(data=data.frame(age_i=age_i,proxy_i=proxy_i),
                        mapping=aes(x=age_i,y=proxy_i),col=color)
}
library(dplyr)
agestarts[nevents]=last(results$data$age)
ggp = ggp + geom_vline(xintercept = agestarts,col="black",size=0.15)
print(ggp)
# ggsave("proxyplot-4800x2000.eps", device=cairo_ps,width=4800,height=2000,units="px",dpi=500,limitsize=FALSE)

@@

```{r unconstrained}
{
  library(matrixStats)
  library(ggplot2)

@@

```{r fixed, eval=TRUE}
library(INLA)
fixedsims = cbind(#rep(inla.mmarginal(adolphipdfs$tie1),nsims),
                  rep(inla.mmarginal(adolphipdfs$tie2),nsims),
                  rep(inla.mmarginal(adolphipdfs$tie3),nsims),
                  rep(inla.mmarginal(adolphipdfs$tie4),nsims),
                  rep(inla.mmarginal(adolphipdfs$tie5),nsims)
                  )
synchronization = list(samples = fixedsims,nsims=nsims,
                       locations=c(#1492.50,
                                   1502.80,1532.70,1767.25,2132.40),
                       locations_unit="depth")
results_fixed = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                synchronization=synchronization,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=TRUE) ,
                print.progress=TRUE
                )
{
  gicc05=results_fixed$original.chron$age[1+1:n]
  ggd = data.frame(depth=results_fixed$data$depth,
                   mean=results_fixed$simulation$summary_sync$mean-gicc05,
                   lower=results_fixed$simulation$summary_sync$lower-gicc05,
                   upper=results_fixed$simulation$summary_sync$upper-gicc05,
                   zeros = numeric(n))
  ggp = ggplot(data=ggd,aes(x=depth)) + theme_bw()+
    #geom_line(aes(y=zeros),color="gray",linetype="dashed")+
    geom_line(aes(y=mean),col="blue")+
    geom_ribbon(aes(ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    xlab("Depth (m)") + ylab("Simulated time scale - GICC05 (years)")
  print(ggp)

@@

## Uncertain tie-points

Synchronizing our chronologies with the Adolphi tie-points where the uncertainties is incorporated can be done using Monte Carlo simulations. All of this can be done using the bremla function.

@@

Excluding the contested fourth tie-point can be done as follows:
```{r sync2, eval = TRUE}
library(ggplot2)
library(INLA)
synchronization = list(method="adolphi",nsims=nsims,
                       locations=c(NA,1502.80,1532.70,NA,2132.40),
                       locations_unit="depth")
results_sync2 = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                synchronization=synchronization,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=TRUE,summary=list(CI.type="hpd")) ,
                print.progress=TRUE
                )
tiepointranges = as.data.frame(matrix(NA,nrow=3,ncol=3))
gicc05=results_sync2$original.chron$age[1+1:n]
gicc05tie = gicc05[results_sync2$tie_points$locations_indexes]
colnames(tiepointranges)=c("lower","upper","depth")
for(i in 1:3){
  tiepointranges[i,1:2] = inla.hpdmarginal(0.95,adolphipdfs[[paste0("tie",c(2,3,5)[i])]])-gicc05tie[i]
}
tiepointranges[,3] = depth[results_sync2$tie_points$locations_indexes]
{

  ggd = data.frame(depth=results_sync2$data$depth,
                   mean=results_sync2$simulation$summary_sync$mean-gicc05,
                   lower=results_sync2$simulation$summary_sync$lower-gicc05,
                   upper=results_sync2$simulation$summary_sync$upper-gicc05,
                   zeros = numeric(n))
  ggp = ggplot(data=ggd,aes(x=depth)) + theme_bw()+
    #geom_line(aes(y=zeros),color="gray",linetype="dashed")+
    geom_line(aes(y=mean),col="blue")+
    geom_ribbon(aes(ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    xlab("Depth (m)") + ylab("Simulated time scale - GICC05 (years)") +
    geom_linerange(data=tiepointranges,aes(x=depth,ymin=lower,ymax=upper),color="magenta")
  print(ggp)

  # ggsave("sync-no4-4800x2000.eps", device=cairo_ps,width=4800,height=2000,units="px",dpi=500,limitsize=FALSE)
}
```

@@

```{r events_individual, eval=FALSE}
library(stringr)
eventnumber=13 #number between 1 and 29. specifies which transition to consider
#load data window and specifics to transition
lowerints = which.index(event_intervals$depth_int_lower.m, depth[2:length(depth)])
upperints = which.index(event_intervals$depth_int_upper.m, depth[2:length(depth)])
depth.reference = event_intervals$NGRIP_depth_m[eventnumber]
age.reference = event_intervals$GICC_age.yb2k[eventnumber]
interval = lowerints[eventnumber]:upperints[eventnumber]
transitionlabel = str_sub(event_intervals$onsetlabel[eventnumber],
                      str_locate(event_intervals$onsetlabel[eventnumber],"GI")[1])
control.linramp=list(proxy=proxy,
                     interval=interval,
                     interval.unit="index",
                     depth.reference=event_intervals$NGRIP_depth_m[eventnumber]
                     )
results_event = linrampfitter(results_sync,control.linramp)
control.transition_dating = list(label="Simulated transition")
results_event = events_depth_to_age(results_event,
                                    control.transition_dating=control.transition_dating)
results_event0 = linrampfitter(results,control.linramp)
results_event0 = events_depth_to_age(results_event0,
                                    control.transition_dating=control.transition_dating)
results_event2 = linrampfitter(results_sync2,control.linramp)
results_event2 = events_depth_to_age(results_event2,
                                    control.transition_dating=control.transition_dating)
{
  ggd1 = data.frame(depth=depth[interval],proxy=proxy[interval],
                    x=results_event$linramp$data$x,
                    mean=results_event$linramp$linrampfit$mean,
                    lower=results_event$linramp$linrampfit$q0.025,
                    upper=results_event$linramp$linrampfit$q0.975
                    )
  gg1 = ggplot(data=ggd1,aes(x=depth))+geom_line(aes(y=proxy),col="gray")+
    theme_bw()+ xlim(rev(range(depth[interval])))+xlab("Depth (m)")+
    ylab(expression(paste(delta^18,"O (permil)")))+ggtitle("(a) GI-11 Linear ramp fit")+
    geom_ribbon(aes(x=x,ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    geom_line(aes(x=x,y=mean),col="blue",size=0.7)

@@

}

{

  tiepointranges_full = as.data.frame(matrix(NA,nrow=4,ncol=3))
gicc05=results_sync$original.chron$age[1+1:n]
gicc05tie = gicc05[results_sync$tie_points$locations_indexes]
colnames(tiepointranges)=c("lower","upper","depth")
for(i in 1:4){
  tiepointranges_full[i,1:2] = inla.hpdmarginal(0.95,adolphipdfs[[paste0("tie",c(2,3,4,5)[i])]])-gicc05tie[i]
}
tiepointranges_full[,3] = depth[results_sync$tie_points$locations_indexes]
colnames(tiepointranges_full) = c("lower","upper","depth")

  ggd = data.frame(depth=results_sync2$data$depth,
                   mean0=results$simulation$summary$mean-gicc05,
                   lower0=results$simulation$summary$lower-gicc05,
                   upper0=results$simulation$summary$upper-gicc05,
                   mean=results_sync$simulation$summary_sync$mean-gicc05,
                   lower=results_sync$simulation$summary_sync$lower-gicc05,
                   upper=results_sync$simulation$summary_sync$upper-gicc05,
                   mean2=results_sync2$simulation$summary_sync$mean-gicc05,
                   lower2=results_sync2$simulation$summary_sync$lower-gicc05,
                   upper2=results_sync2$simulation$summary_sync$upper-gicc05,
                   zeros = numeric(n))
  ggp = ggplot(data=ggd,aes(x=depth)) + theme_bw()+
    #geom_line(aes(y=zeros),color="gray",linetype="dashed")+
    geom_ribbon(aes(ymin=lower0,ymax=upper0),fill="cyan2",col="cyan2",alpha=0.3)+
    geom_line(aes(y=mean0),col="brown")+
    geom_ribbon(aes(ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    geom_line(aes(y=mean),col="blue")+
    xlab("Depth (m)") + ylab("Simulated time scale - GICC05 (years)") +
    ggtitle("(a) Simulated chronologies")+
    geom_linerange(data=tiepointranges_full,aes(x=depth,ymin=lower,ymax=upper),color="magenta")
  print(ggp)

  ggp1 = ggplot(data=ggd,aes(x=depth)) + theme_bw()+
    #geom_line(aes(y=zeros),color="gray",linetype="dashed")+
    geom_ribbon(aes(ymin=lower2,ymax=upper2),fill="cyan2",col="cyan2",alpha=0.3)+
    geom_line(aes(y=mean2),col="brown")+
    geom_ribbon(aes(ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    geom_line(aes(y=mean),col="blue")+
    xlab("Depth (m)") + ylab("Simulated time scale - GICC05 (years)") +
    ggtitle("(a) Synchronized chronologies")+
    geom_linerange(data=tiepointranges_full,aes(x=depth,ymin=lower,ymax=upper),color="magenta")
  print(ggp1)

   ggd1 = data.frame(depth=depth[interval],proxy=proxy[interval],
                    x=results_event$linramp$data$x,
                    mean=results_event$linramp$linrampfit$mean,
                    lower=results_event$linramp$linrampfit$q0.025,
                    upper=results_event$linramp$linrampfit$q0.975
                    )
  gg1 = ggplot(data=ggd1,aes(x=depth))+geom_line(aes(y=proxy),col="gray")+
    theme_bw()+ 
    #xlim(rev(range(depth[interval])))+
    xlim(c(2161,2155.3))+
    xlab("Depth (m)")+
    ylab(expression(paste(delta^18,"O (permil)")))+ggtitle("(b) GI-11 Linear ramp fit")+
    geom_ribbon(aes(x=x,ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    geom_line(aes(x=x,y=mean),col="blue",size=0.7)

  ybottom = min(results_event$linramp$data$y)
  ytop = min(results_event$linramp$linrampfit$q0.025)
  margt0=results_event$linramp$param$t0$marg.t0
  normt0.y = margt0[,2]/diff(range(margt0[,2]))*(ytop-ybottom)-min(margt0[,2])+ybottom
  gg1 = gg1 + geom_line(data=data.frame(x=margt0[,1],y=normt0.y),aes(x=x,y=y),col="brown",size=1.0)

  gghist = ggplot(data = data.frame(ages=results_event$event_dating$samples)) + theme_bw()+
    geom_histogram(aes(x=ages,y=..density..),fill="orange",col="black")+xlab("Onset age (yb2k)")+
    ylab("Density") + ggtitle("(c) GI-11 Onset age") +
    geom_vline(aes(xintercept = age.reference),lty=3,size=0.8)+
    # geom_vline(aes(xintercept=results_event$event_dating$mean),col="blue",size=0.7)+
    # geom_vline(aes(xintercept=results_event$event_dating$q0.025),col="red",size=0.7)+
    # geom_vline(aes(xintercept=results_event$event_dating$q0.975),col="red",size=0.7)+
    xlim(rev(range(results_event$event_dating$samples)))

  library(stringr)

ggl = ggplot(data.frame(x=c(1,2),y=c(2,3),x1=c(1,2),y1=c(1,2),x2=c(1,2),y2=c(1,2)),
             x3=c(1,2),y3=c(2,3),x4=c(1,2),y4=c(1,2),x5=c(1,2),y5=c(1,2),x6=c(1,2),x7=c(1,2),
             x8 = c(1,2), y8=c(1,2)) +
  geom_line(aes(x=x,y=y,col="Synchronous chronology mean"))+
  geom_line(aes(x=x1,y=y1,col="Synchronous chronology 95% CI"))+
  geom_line(aes(x=x2,y=y2,col="Unsynchronous chronology mean"))+
  geom_line(aes(x=x,y=y,col="Unsynchronous chronology 95% CI"))+
  geom_line(aes(x=x,y=y,col="Tie point 95% CI"))+
  scale_color_manual("",values=c("Synchronous chronology mean"="blue",
                                "Synchronous chronology 95% CI"="red",
                                "Unsynchronous chronology mean"="brown",
                                "Unsynchronous chronology 95% CI"="cyan2",
                                "Tie point 95% CI"="magenta"),
                       breaks=c("Synchronous chronology mean",
                                "Synchronous chronology 95% CI",
                                "Unsynchronous chronology mean",
                                "Unsynchronous chronology 95% CI",
                                "Tie point 95% CI")
                                 )+
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = c(0.5, 0.5), # move the legend to the center
        legend.title = element_blank(),
        # legend.text = element_text(size = 17),
        legend.key = element_rect(fill='NA'),
        legend.key.width=unit(1,"cm"),
        # legend.key.size = unit(0.8,'cm'),
        panel.grid = element_blank(),
        # legend.spacing = unit(3,'cm'),
        # legend.spacing.y = unit(0.5,'cm'),
        panel.border = element_rect(colour = "white", fill='white', size=1)
  )

ggl1 = ggplot(data.frame(x=c(1,2),y=c(2,3),x1=c(1,2),y1=c(1,2),x2=c(1,2),y2=c(1,2)),
             x3=c(1,2),y3=c(2,3),x4=c(1,2),y4=c(1,2),x5=c(1,2),y5=c(1,2),x6=c(1,2),x7=c(1,2),
             x8 = c(1,2), y8=c(1,2)) +
  geom_line(aes(x=x,y=y,col="\n(a) Chronology mean\n(b) Linear ramp mean\n"))+
  geom_line(aes(x=x1,y=y1,col="(a) Chronology 95% CI\n(b) Linear ramp 95% CI"))+
  geom_line(aes(x=x2,y=y2,col="\n(a) Chronology mean, tie point 4 excluded\n(b) Onset posterior distribution\n"))+
  geom_line(aes(x=x,y=y,col="(a) Chronology 95% CI, tie point 4 excluded"))+
  geom_line(aes(x=x,y=y,col="\n(a) Tie point 95% CI\n"))+
  geom_line(aes(x=x,y=y,col="(b) d18O data"))+
  scale_color_manual("",values=c("\n(a) Chronology mean\n(b) Linear ramp mean\n"="blue",
                                "(a) Chronology 95% CI\n(b) Linear ramp 95% CI"="red",
                                "\n(a) Chronology mean, tie point 4 excluded\n(b) Onset posterior distribution\n"="brown",
                                "(a) Chronology 95% CI, tie point 4 excluded"="cyan2",
                                "\n(a) Tie point 95% CI\n"="magenta",
                                "(b) d18O data"="gray"),
                       breaks=c("\n(a) Chronology mean\n(b) Linear ramp mean\n",
                                "(a) Chronology 95% CI\n(b) Linear ramp 95% CI",
                                "\n(a) Chronology mean, tie point 4 excluded\n(b) Onset posterior distribution\n",
                                "(a) Chronology 95% CI, tie point 4 excluded",
                                "\n(a) Tie point 95% CI\n",
                                "(b) d18O data")
                                 )+
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = c(0.5, 0.5), # move the legend to the center
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        legend.key = element_rect(fill='NA'),
        legend.key.width=unit(1,"cm"),
        # legend.key.height=unit(0.3,"cm"),
        # legend.key.size = unit(17,'cm'),
        panel.grid = element_blank(),
        # legend.spacing = unit(3,'cm'),
        # legend.spacing.y = unit(1.5,'cm'),
        panel.border = element_rect(colour = "white", fill='white', size=1)
  )

  #(a) (b) and (c) legends in same legend (maybe such that blue means something in a and something in b etc)
  plots = c()
  plots[[1]] = ggp
  plots[[2]] = ggl
  plots[[3]] = gg1
  plots[[4]] = gghist

  ggarrange(plotlist=plots,nrow=2,ncol=2)
  # ggsave("multiplot-unsync-3000x2000.eps",device=cairo_ps,width=3000,height=2000,units="px",limitsize=FALSE)

  plots1 = c()
  plots1[[1]] = ggp1
  plots1[[2]] = ggl1
  plots1[[3]] = gg1
  plots1[[4]] = gghist

  ggarrange(plotlist=plots1,nrow=2,ncol=2,widths = c(0.67,0.5,0.5,0.5))
  plotrow1 = c()
  plotrow1[[1]] = ggp1
  plotrow1[[2]] = ggl1
  plotrow2 = c()
  plotrow2[[1]] = gg1
  plotrow2[[2]] = gghist
  ggarow1 = ggarrange(plotlist=plotrow1,widths=c(0.7,0.3))
  ggarow2 = ggarrange(plotlist=plotrow2)

  ggarrange(c(ggarow1,ggarow2),nrow=2)

  ggarrange(plotlist= c(ggarrange(plotlist=plotrow1,widths=c(0.67,0.33)),
            ggarrange(plotlist=plotrow1,widths=c(0.5,0.5))) )
  # ggsave("multiplot-sync-no4-2200x4000.eps",device=cairo_ps,height=2200,width=4000,units="px",limitsize=FALSE)
  #

}

```{r multifig-all, eval=FALSE}

eventdepth = results_event$linramp$param$t0$mean
  tiepointranges_full = as.data.frame(matrix(NA,nrow=4,ncol=3))
gicc05=results_sync$original.chron$age[1+1:n]
gicc05tie = gicc05[results_sync$tie_points$locations_indexes]
colnames(tiepointranges)=c("lower","upper","depth")
for(i in 1:4){
  tiepointranges_full[i,1:2] = inla.hpdmarginal(0.95,adolphipdfs[[paste0("tie",c(2,3,4,5)[i])]])-gicc05tie[i]
}
tiepointranges_full[,3] = depth[results_sync$tie_points$locations_indexes]
colnames(tiepointranges_full) = c("lower","upper","depth")

  ggd = data.frame(depth=results_sync2$data$depth,
                   mean0=results$simulation$summary$mean-gicc05,
                   lower0=results$simulation$summary$lower-gicc05,
                   upper0=results$simulation$summary$upper-gicc05,
                   mean=results_sync$simulation$summary_sync$mean-gicc05,
                   lower=results_sync$simulation$summary_sync$lower-gicc05,
                   upper=results_sync$simulation$summary_sync$upper-gicc05,
                   mean2=results_sync2$simulation$summary_sync$mean-gicc05,
                   lower2=results_sync2$simulation$summary_sync$lower-gicc05,
                   upper2=results_sync2$simulation$summary_sync$upper-gicc05,
                   zeros = numeric(n))

  ggp = ggplot(data=ggd,aes(x=depth)) + theme_bw()+
    coord_cartesian(ylim=c(range(ggd$lower0,ggd$upper))) +
    #geom_line(aes(y=zeros),color="gray",linetype="dashed")+
    geom_ribbon(aes(ymin=lower0,ymax=upper0),fill="black",col="black",alpha=0.3)+
    geom_ribbon(aes(ymin=lower2,ymax=upper2),fill="red",col="red",alpha=0.3)+
    geom_ribbon(aes(ymin=lower,ymax=upper),fill="blue",col="blue",alpha=0.3)+
    geom_line(aes(y=mean0),col="black",size=0.9)+
    geom_line(aes(y=mean2),col="red",size=0.9)+
    geom_line(aes(y=mean),col="blue",size=0.9)+
    xlab("Depth (m)") + ylab("Simulated time scale - GICC05 (years)") +
    ggtitle("(a) Simulated chronologies")+
    geom_linerange(data=data.frame(depth=eventdepth),
                   aes(x=depth,ymin=-500,ymax=1000),
                   col="magenta",size=0.8)+
    geom_linerange(data=tiepointranges_full,aes(x=depth,ymin=lower,ymax=upper),color="green",
                   size=0.8)
  print(ggp)

  ggp1 = ggplot(data=ggd,aes(x=depth)) + theme_bw()+
    #geom_line(aes(y=zeros),color="gray",linetype="dashed")+
    geom_ribbon(aes(ymin=lower2,ymax=upper2),fill="cyan2",col="cyan2",alpha=0.3)+
    geom_line(aes(y=mean2),col="black")+
    geom_ribbon(aes(ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    geom_line(aes(y=mean),col="blue")+
    xlab("Depth (m)") + ylab("Simulated time scale - GICC05 (years)") +
    ggtitle("(a) Synchronized chronologies")+
    geom_linerange(data=tiepointranges_full,aes(x=depth,ymin=lower,ymax=upper),color="magenta")
  print(ggp1)

   ggd1 = data.frame(depth=depth[interval],proxy=proxy[interval],
                    x=results_event$linramp$data$x,
                    mean=results_event$linramp$linrampfit$mean,
                    lower=results_event$linramp$linrampfit$q0.025,
                    upper=results_event$linramp$linrampfit$q0.975,
                    mean0=results_event0$linramp$linrampfit$mean,
                    lower0=results_event0$linramp$linrampfit$q0.025,
                    upper0=results_event0$linramp$linrampfit$q0.975,
                    mean2=results_event2$linramp$linrampfit$mean,
                    lower2=results_event2$linramp$linrampfit$q0.025,
                    upper2=results_event2$linramp$linrampfit$q0.975
                    )
  gg1 = ggplot(data=ggd1,aes(x=depth))+geom_line(aes(y=proxy),col="gray")+
    theme_bw()+ 
    #xlim(rev(range(depth[interval])))+
    xlim(c(2161,2155.3))+
    xlab("Depth (m)")+
    ylab(expression(paste(delta^18,"O (permil)")))+ggtitle("(b) GI-11 Linear ramp fit")+
    geom_ribbon(aes(x=x,ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    geom_line(aes(x=x,y=mean),col="blue",size=0.7)

  ybottom = min(results_event$linramp$data$y)
  ytop = min(results_event$linramp$linrampfit$q0.025)
  margt0=results_event$linramp$param$t0$marg.t0
  normt0.y = margt0[,2]/diff(range(margt0[,2]))*(ytop-ybottom)-min(margt0[,2])+ybottom
  gg1 = gg1 + geom_line(data=data.frame(x=margt0[,1],y=normt0.y),aes(x=x,y=y),col="black",size=1.0)
